\documentclass[''urlcolor=red'']{beamer}
\usepackage{hyperref}
\usetheme{Warsaw}
\title{Towards Social Semantic tools}
\author{Arvind}
\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Towards Social Semantic tools}
  \begin{block}{Big data}
    \begin{itemize}
    \item Every single blog post/tweet/status update that you make adds up as well as generates big data to be piled up on the Web.
    \item All that big data on the Web lacks inter-connectivity. Say for example you tweet a link to a friend of yours in which you also say that the phone number in that page is wrong and here is the correct number.
    \item The experience of Web will be enriched if another user, not a friend of yours, at the page could also see the correction.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Towards Social Semantic tools}
  \begin{block}{Implementation}
    \begin{itemize}
    \item A browser extension will help users in marking and consume annotations/comments for a page.
    \item User A marks bar on page foobar as a comment for page foo.  User B can see the comments on page foo, without ever going to foobar.
    \item Consider \url{http://jace.zaiki.in/2012/06/26/technology-outsource-vs-open-source}, where the author says for discussion go to a different link.
    \item A user having the extension would be able to see the comments on that page itself, rather than having to go to another page.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Towards Social Semantic tools}
  \begin{block}{Extending the idea towards digital heritage}
    \begin{itemize}
    \item Look at the mural \url{http://folkhampi.openrun.net/muraldemo.html}.
    \item What if someone comments on twitter saying ``Hey look this mural is similar to the ones found in Egypt.''.
    \item During a virtual walk comments/annotations show up if present.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Towards Social Semantic tools}
  \begin{block}{Links}
    \begin{itemize}
    \item \url{http://a11y.in}
    \item \url{http://alipi.janastu.org}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Thank You}
  \begin{center}
    Thank You!\\
  \end{center}
\end{frame}

\end{document}
